Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-30 WSSSPE2_report/WSSSPE2_review.tex
Added First breakout discussion notes from Reproducibility group

@@

>>>>

This group discussed five papers with a wide variety ideas of how to support reproducibility and reuse. It focussed on identifying concrete that the attendees could work together on, which would have a positive effect on the community.

@@

In the first discussion session, this group broke up into two smaller groups working on different topics: Reproducibility, and Reuse and Sharing.

\subsubsection{First breakout discussion: Reproducibility group}

The first group discussed ways in which reproducibility of papers could be improved. A consensus surrounded the provision of examples: demonstrating to others how to achieve reproducibility. Major public funding investments go into research that heavily relies on software to be reproducible, hence lack thereof is raising major concerns.

Two main avenues could be used to implement policy that would improve reproducibility and drive top-down culture change: 
\begin{itemize}
\item Funders can aim to get more software expertise on to funding review panels and provide more guidance on what is required of software related to research (cf. data management plans)
\item Journals can define and publish journal policies to improve reproducibility, and reviewers can insist that authors provide sufficient information and access to data and software to allow them reproduce the results in the paper. Stronger policies even for some high-impact journals have recently come into place, for example Nature Publishing journals.
\end{itemize}

If journals do enforce greater reproducibility constraints, it is important to lower the barriers to reviewers attempting to verifying the correctness of the software used to generate the results. A major issue is that a lot of software only builds on certain systems. Should journals provide more tools / support for reviewers, and if so, what is it? An idea that came from the groups was to define a set of support services that should be available to software paper reviewers. Another was to provide the ability for reviewers to flag the requirement for a ?software verification?, similar to ability to flag that a paper needs to be seen by a statistician.

Other discussion focussed on ways in which researchers themselves could improve the reproducibility of research. One way would be to establish tracks at conferences that subject papers to reproduction, which for those that pass would lend them an additional badge (similar to OOPSLA). Another is simply to get more people to use your software: for instance by outreach to high school students - can your software be used by them? Finally, there is a role for community-curated benchmarks to validate the performance and capabilities of tools.

\subsubsection{First breakout discussion: Reuse and Sharing group}
